Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

We choose to subset the data to users who have listened to more than 27 songs and songs which were listened to by more than 22 users. This resulted in a datset which was 10\% the size of the original. Despite subsetting the data, we are still dealking with a matrix of $8130$ users by $11861$, so our algorithms will take a fair amount of time to run.

>>>>

We choose to subset the data to users who have listened to more than 27 songs and songs which were listened to by more than 22 users. This resulted in a datset which was 10\% the size of the original. Despite subsetting the data, we are still dealing with a matrix of $8130$ users by $11861$ songs, so our algorithms will take a fair amount of time to run.
